### 2016-03-17 ch05-initvals/initial-values.tex
Listing format improved
Different figure names per chapter
Externalize tables in CH05

\chapter{Initialization of parametric estimators}
\label{sec:initvals}
\myEpigraph{Everything starts somewhere, though many physicists disagree. But people have always been dimly aware of the problem with the start of things. They wonder how the snowplough driver gets to work, or how the makers of dictionaries look up the spelling of words.}{Terry Pratchett}{Hogfather}
\gdef\thisDir{ch05-initvals}
\researchBasedOn{Geerardyn2015TIM}

@@

\begin{table}[p]
  \centering
  \caption{Observed percentiles of the cost function $V(\model{\bullet}$).}
% \input{\thisDir/table1.tex}
\pgfplotstabletypeset[precision=0]{
method            P000     P025     P050      P075       P100   
\model{VXI}       4354.83  4442.31  4493.52   4706.61    9633.53
\model{exist}     4345.3   4525.82  8740.54  12413.3    29236.5
\model{trunc}     4335.68  4476.29  4841.74   8130.28   88308.1
\model{RFIR}      4328.93  4422.11  4468.8    4716.46    9606.54
\model{best}      4328.93  4414.87  4457.91   4644.07    8569.93 
}
  \label{tbl:costMeasurements}
\end{table}

@@

\begin{figure}[p]
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \setlength{\figurewidth}{0.75\columnwidth}
  \input{\thisDir/fig/meas-validation.tikz}
  \caption[Validation cost of the different measurements.]{Validation of the measured models. 
  For each method, the distance \eqref{eq:measurementCriterion} between the estimates and $\model{VXI}$ is shown~\legref{leg:validationMeasurements:best:data} together with the median~\legref{leg:validationMeasurements:best:median} and inter-quartile range~\legref{leg:validationMeasurements:best:iqr}.
  $\norm{G_{\mathrm{VXI}}}$\legref{leg:validationMeasurements:H2Norm} is shown as a reference.
  The bottom plot shows a zoom of the top plot.
  The proposed methods yield models that are closer to $\model{VXI}$ than the existing $\model{exist}$.
  The results are in line with the values of the cost function in \figref{fig:costMeasurements}.}
  \label{fig:validationMeasurements}
\end{figure}
\begin{table}[p]
  \centering
  \caption{Observed percentiles of the validation distance $\norm{\model{\bullet}-G_{\mathrm{VXI}}}$.}
% \input{\thisDir/table2.tex}
\pgfplotstabletypeset[zerofill=true,precision=2]{
method              P000      P025      P050        P075     P100   
\model{VXI}         0.47325   0.916589   1.06396   1.29177   2.4089
\model{exist}       1.48252   1.88392   13.7177   19.3113   26.7984
\model[init]{trunc} 1.35399   2.72412   14.9431   24.7154   85.3351
\model{trunc}       1.27344   1.71872    2.34574  13.0301   63.8373
\model[init]{RFIR}  1.10525   1.61051    1.7778    2.00318  18.211
\model{RFIR}        1.20554   1.57398    1.72416   1.84941   4.55004
\model{best}        1.20554   1.55725    1.72059   1.84593  15.0063
}
\label{tbl:validationMeasurements}
\end{table}

@@

\begin{table}
  \centering
  \caption{Overview of the test cases for the initialization stress test.}
\begin{tabular}{crlrrrrr}
\toprule
\textsc{Case}   &  \multicolumn{2}{c}{\textsc{Filter}}   &  $\true{\successRate} [\%]$  &  $\successRate_{\mathrm{exist}} [\%]$ &  $\successRate_{\mathrm{trunc}} [\%]$   &  $\successRate_{\mathrm{RFIR}} [\%]$  &  $\successRate_{\mathrm{best}} [\%]$ \\
\midrule
1  &  {Chebyshev I}  &  low-pass   & 100 & 100 & 95  & 100 & 100\\
2  &  {Chebyshev I}  &  band-pass   & 100 & 14  & 7 & 16  & 34\\
3  &  {Chebyshev I}  &  high-pass     & 100 & 100 & 96  & 100 & 100\\
4  &  {Chebyshev I}  &  band-stop     & 100 & 40  & 28  & 74  & 90\\
5  &  {Chebyshev II}   &  low-pass     & 100 & 98  & 73  & 100 & 100\\
6  &  {Chebyshev II}   &  band-pass     & 100 & 23  & 16  & 70  & 79\\
7  &  {Chebyshev II}   &  high-pass     & 100 & 97  & 74  & 100 & 100\\
8  &  {Chebyshev II}   &  band-stop     & 16  & 0 & 0 & 0 & 0\\
9  &  Elliptical   &  low-pass     & 100 & 83  & 34  & 95  & 98\\
10   &  Elliptical   &  band-pass     & 100 & 0 & 0 & 2 & 1\\
11   &  Elliptical   &  high-pass     & 100 & 83  & 33  & 97  & 100\\
12   &  Elliptical   &  band-stop     & 0 & 0 & 0 & 0 & 0\\
13   &  Butterworth  &  low-pass     & 100 & 100 & 100 & 100 & 100\\
14   &  Butterworth  &  band-pass     & 100 & 100 & 100 & 100 & 100\\
15   &  Butterworth  &  high-pass     & 100 & 100 & 100 & 100 & 100\\
16   &  Butterworth  &  band-stop     & 100 & 100 & 100 & 100 & 100\\
\bottomrule
\end{tabular}
\label{tbl:init:stresstest}
\end{table}

@@

\begin{figure}[p]
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \centering
  \input{\thisDir/fig/bodeplots.tikz}
  \caption[Bode plots of the stress test filters.]{Bode plots of the tested filters~\legref{leg:bode:true} in the stress test. 
  For each filter, two (randomly selected) instances of the parametric estimates $\model{\bullet}$ are shown per method.
  % Top to bottom: Chebyshev I, Chebyshev II, Elliptical and Butterworth characteristic.
  % Left to right: low-pass, band-pass, high-pass and band-stop.
  }
  \label{fig:bodeplots}
\end{figure}

@@

\begin{table}
  \centering
  \centering
  \caption{Observed timing of the different estimation steps.}
% \input{\thisDir/table2.tex}
\pgfplotstabletypeset[zerofill=true,string replace={nan}{},precision=0,relative*=0,empty cells with={\deemph{--}}, %round to 1 ms
    columns/method/.style={string type,column type=l,column name={\textsc{Method}}},
    columns/Q/.style={column type=c,column name={$Q\axisunit{dB}$},zerofill=false},
    columns/NBW/.style={column type=c,column name={$N_{3\unit{dB}}$},zerofill=false},
    columns/tsmooth/.style={column type=r,column name={$t_{\mathrm{smooth}} \axisunit{ms}$},multiply by=1000},
    columns/tinit/.style={column type=r,column name={$t_{\mathrm{init}} \axisunit{ms}$},multiply by=1000},
    columns/tfinal/.style={column type=r,column name={$t_{\mathrm{final}} \axisunit{ms}$},multiply by=1000},
]{%
Q  NBW  method  tsmooth    tinit  tfinal
 % 6  36  \model{\trueSymbol}    nan     nan     0.197034 
 % 6  36  \model{exist}   nan     nan     0.159937 
 6  36  \model{trunc}   0.745073    0.0623485   0.163107 
 6  36  \model{RFIR}    6.79873     0.0774866   0.175263 
 % 6  48  \model{\trueSymbol}    nan     nan     0.209216 
 % 6  48  \model{exist}   nan     nan     0.206823 
 6  48  \model{trunc}   1.00383     0.0902347   0.208173 
 6  48  \model{RFIR}    6.18632     0.0910651   0.221194 
% 20  36  \model{\trueSymbol}    nan     nan     0.445936 
% 20  36  \model{exist}   nan     nan     0.429752 
20  36  \model{trunc}   4.83667     0.225876    0.454757 
20  36  \model{RFIR}    6.92575     0.253981    0.482431 
% 20  48  \model{\trueSymbol}    nan     nan     0.467081 
% 20  48  \model{exist}   nan     nan     0.457577 
20  48  \model{trunc}   6.59726     0.312937    0.461114 
20  48  \model{RFIR}    8.05168     0.312297    0.468905 
}
\label{tbl:init:timing}
\end{table}

>>>>

\chapter{Initialization of parametric estimators}
\label{sec:initvals}
\myEpigraph{Everything starts somewhere, though many physicists disagree. But people have always been dimly aware of the problem with the start of things. They wonder how the snowplough driver gets to work, or how the makers of dictionaries look up the spelling of words.}{Terry Pratchett}{Hogfather}
\gdef\thisDir{ch05-initvals}
\tikzsetfigurename{ch05fig}
\researchBasedOn{Geerardyn2015TIM}

@@

\begin{table}[p]
  \centering
  \caption{Observed percentiles of the cost function $V(\model{\bullet}$).}
  \input{\thisDir/tables/meas-cost-quantiles.tbl.tex}
  \label{tbl:costMeasurements}
\end{table}

@@

\begin{figure}[p]
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \setlength{\figurewidth}{0.75\columnwidth}
  \input{\thisDir/fig/meas-validation.tikz}
  \caption[Validation cost of the different measurements.]{Validation of the measured models. 
  For each method, the distance \eqref{eq:measurementCriterion} between the estimates and $\model{VXI}$ is shown~\legref{leg:validationMeasurements:best:data} together with the median~\legref{leg:validationMeasurements:best:median} and inter-quartile range~\legref{leg:validationMeasurements:best:iqr}.
  $\norm{G_{\mathrm{VXI}}}$\legref{leg:validationMeasurements:H2Norm} is shown as a reference.
  The bottom plot shows a zoom of the top plot.
  The proposed methods yield models that are closer to $\model{VXI}$ than the existing $\model{exist}$.
  The results are in line with the values of the cost function in \figref{fig:costMeasurements}.}
  \label{fig:validationMeasurements}
\end{figure}
\begin{table}[p]
  \centering
  \caption{Observed percentiles of the validation distance $\norm{\model{\bullet}-G_{\mathrm{VXI}}}$.}
  \input{\thisDir/tables/meas-validation-quantiles.tbl.tex}
\label{tbl:validationMeasurements}
\end{table}

@@

\begin{table}
  \centering
  \caption{Overview of the test cases for the initialization stress test.}
  \input{\thisDir/tables/stresstest-cases.tbl.tex}
\label{tbl:init:stresstest}
\end{table}

@@

\begin{figure}[p]
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \centering
  \input{\thisDir/fig/bodeplots.tikz}
  \caption[Bode plots of the stress test filters.]{Bode plots of the tested filters~\legref{leg:bode:true} in the stress test. 
  For each filter, two (randomly selected) instances of the parametric estimates $\model{\bullet}$ are shown per method.
  }
  \label{fig:bodeplots}
\end{figure}

@@

\begin{table}
  \centering
  \caption{Observed timing of the different estimation steps.}
  \input{\thisDir/tables/timings.tbl.tex}
\label{tbl:init:timing}
\end{table}
